---
title: "Other"
format: 
  html:
    self-contained: true
    toc: true
    toc-title: "My contents"
    toc-location: left
    theme: 
      light: minty
      dark: superhero
    fontsize: 20px
lang: en
bibliography: references.bib
citation-location: margin
code-annotations: hover
---

```{r}
#| include: false
library(readr)
library(ggplot2)
#install.packages("DT")
library(DT)
data <- read_csv("Data/dataset.csv")
```


```{r}
#| code-fold: true
#| code-summary: see this specific code
#| echo: false
head(data)
```

```{r}
#| code-fold: true
#| code-summary: see this specific code
#| echo: true
head(data)
```

```{r}
#| code-fold: true
#| code-summary: see this specific code
#| echo: fenced
head(data)
```

```{r}
#| code-fold: true
#| code-summary: see this specific code
#| echo: fenced
str(data)
```


```{r}
#| code-fold: true
#| code-summary: see this specific code
#| echo: true
summary(data)
```

```{r}
#| code-fold: true
#| code-summary: see this specific code
#| echo: fenced
summary(data)
```

Table of the data for anxiety and flexibility

@tbl-chap illustrates the characteristics of the population of interest
```{r}
#| label: tbl-chap
#| tbl-cap: "Characteristics of population"
#| lst-label: lst-table1
#| lst-cap: Basic use of the kable() function
knitr::kable(head(data))
```

@lst-table1 illustrates a basic use of the kable() function

Correlation between anxiety and flexibility stratified based on mindfulness

@lst-plot1 illustrates a basic use of the function plot()

```{r}
#| message: false
#| error: false
#| warning: false
#| code-fold: true
#| code-summary: see this specific code
#| out-width: 50%                                
#| fig-align: center                             
#| fig-cap: Correlation between anxiety and flexibility stratified based on mindfulness
#| fig-cap-location: margin
#| label: fig-plot1
#| lst-label: lst-plot1
#| lst-cap: Basic use of the plot() function
ggplot(data,
       aes(x=flexibility, y=anxiety, color=mindfulness)) +
  geom_point()
```



Figure and table
```{r}
#| echo: false
#| fig-column: margin

ggplot(data,
       aes(x=flexibility, y=anxiety, color=mindfulness)) +
  geom_point()+
  geom_smooth(formula = y ~ x, method = "loess") +
  theme(legend.position = 'bottom')

datatable(data, options = list(pageLength = 5))
```


```{r}
#| eval: true

ggplot(mtcars, 
       aes(hp, mpg, color = factor(am))) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess") +
  theme(legend.position = 'bottom')
```


```{r}
#| eval: true

datatable(mtcars,
  options = list(pageLength = 5))
```


```{r}
#| fig-column: margin

knitr::kable(head(mtcars))

ggplot(mtcars, 
       aes(hp, mpg, color = factor(am))) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess") +
  theme(legend.position = 'bottom')
```




Multiple plots
@fig-plotsModels illustrates different things. @fig-plotsModels-1 illustrates the correlation between anxiety and flexibility, @fig-plotsModels-2 illustrates the polynomial regression model, @fig-plotsModels-3 the Linear regression model, @fig-plotsModels-4 the GLM with Poisson

```{r}
#| label: fig-plotsModels
#| column: screen-inset-shaded
#| warning: false
#| echo: false
#| layout-nrow: 2
#| layout-ncol: 2
#| fig-cap: "One dataset, different models" 
#| fig-subcap:
#|   - "The data"
#|   - "Polynomial"
#|   - "Linear Model"
#|   - "GLM with Poisson" 
#| out-width: 15cm
#| fig-align: center


ggplot(data,
       aes(anxiety, flexibility, size = activity)) +
  geom_point()

ggplot(data,
       aes(anxiety, flexibility, size = activity)) +
  geom_point() + 
  geom_smooth()

ggplot(data,
       aes(anxiety, flexibility, size = activity)) +
  geom_point() + 
  geom_smooth(method = "lm")

ggplot(data,
      aes(anxiety, flexibility, size = activity)) +
  geom_point() + 
  geom_smooth(method = "glm", method.args = list(family = "poisson"))


```

@tbl-tables presents two datasets: @tbl-tables-1 is cars and @tbl-tables-2 is pressure

```{r}
#| label: tbl-tables
#| tbl-cap: "Datasets"
#| warning: false
#| echo: false
#| tbl-subcap: 
#|   - "Cars"
#|   - "Pressure"
#| layout-ncol: 2

knitr::kable(head(cars))

knitr::kable(head(pressure))
```


#Annotation

```{r}
#| echo: true
mtcars %>%                               # <1>
  ggplot( aes(mpg, hp, size = gear)) +   # <2>
  geom_point() +                         # <3>    
  geom_smooth(method = "lm")             # <4>
```

1. This does that
2. This other thing is this
3. And look at this!
4. Please have mercy

The mean of the gear variable in mtcars is `mean(mtcars$gear)`

The mean of the gear variable in mtcars is `r mean(mtcars$gear)`





